\section{Introduction}
This is the report for my Rubik's Cube Solver program. This paper will contain the process of creation behind my project as well as the factors that motivated my decisions behind why I chose the features/aspects/methods that I did.
\subsection{Background}
The Rubik's Cube is a well known puzzle all around the world and it's considered extremely difficult to solve... At least without the helpful guidelines and algorithms that are accessible online. After a gruelling summer of trying to solve the cube via a human algorithm, I want to feel the satisfaction of solving the traditional 3x3x3 cube and hopefully larger versions via computing algorithms. 
\subsection{Aims and Objectives}
The original goal here is to use local search or a constraint solver although it's very likely I could stray to use a different, more efficient and well suited algorithm to solve the cube(s).
\\
A cool feature I'm eager to add is a custom scramble where the user can manually change the digital cube to their real world physical cube's scrambled state then get my program to solve it and provide the algorithm (steps) to solving that particular scramble.
\\
% Needs more info for this section


\subsection{Research Hypothesis}
Although this project is ambitious, I'm hoping that with my current experience and enthusiasm regarding Rubik's Cubes, this project moves forward more fluently than previous projects I've pursued and I'm able to diagnose and solve issues regarding the solving aspect of the project.
\newline
I'm excited to discover if I can create or piece together an algorithm that is versatile enough to solve different sized cubes but considering that I feel this project is a big challenge regarding just the 3x3x3 sized cube, I don't think I'll be too disappointed if I didn't succeed in creating an algorithm that can solve all sized cubes.

\newpage